% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[martin-piegay]{Martin Piegay}

\thinrule

\startblockquote
I am a young software engineer working in
\useURL[url1][https://www.zenika.com/][][Zenika]\from[url1] Lyon (FR). I
code in Java, JavaScript and Golang using several frameworks like Spring
or ReactJS \ldots{} I feel concerned about quality of code and I do my
best to improve it.\crlf
I believe in open-source, I recently contributed to the new reverse
proxy \useURL[url2][https://traefik.io/][][Træfik]\from[url2].
\stopblockquote

\thinrule

\subsection[experience]{Experience}

\startdescription{June 17 - Today}
  {\bf Backend Software Development on Linkysup at
  \useURL[url3][http://www.enedis.fr/compteur-communicant][][Enedis]\from[url3]};
  \useURL[url4][https://www.zenika.com/][][Zenika]\from[url4] Lyon (FR)
\stopdescription

Developing a software for monitoring and remote controlling 35 millions
of electricity meters installed at private individuals.

\startitemize
\item
  Tech: Java 7, JUnit, AssertJ, Mockito, Spring, ZK, SQL/Oracle,
  Mybatis, Elasticsearch, Drools, Apache Kafka, Apache Flume, WebLogic,
  Maven, Git, Jenkins, Bitbucket, Jira, \ldots{}
\item
  Methodology: Agile Scrum, auto organized team with 6 dev/devops and 5
  functional coworkers, experiencing remote working, part of a
  60-coworkers project.
\stopitemize

\startdescription{Dec. 16 - June 17}
  {\bf Fullstack Software Development for Gattefosse};
  \useURL[url5][https://www.zenika.com/][][Zenika]\from[url5] Lyon (FR)
\stopdescription

Developing from scratch a business website which allows clients to
manage medias, users, products and technical documents.

\startitemize
\item
  Backend : Java 8, Spring 4 (Security, Data JPA, MVC), Hibernate,
  Elasticsearch, JUnit, AssertJ, Mockito, Maven
\item
  Frontend : JavaScript ES6, npm, Webpack, ReactJS with Redux,
  Jest/Jasmine, SASS, flexbox
\item
  CMS : Wordpress with custom plugins
\item
  Tech devops : Git, Gitlab with CI, Apache, MySql, Ansible
\item
  Methodology: Agile Scrum, 3 dev, 1 devops, remote clients
\stopitemize

\startdescription{Sept. 16 - Dec. 17}
  {\bf Fullstack Software Development for Grand Frais};
  \useURL[url6][https://www.zenika.com/][][Zenika]\from[url6] Lyon (FR)
\stopdescription

Developing new features on the business specific software to manage
product stock and daily deliveries from warehouse to stores, buying and
billing.

\startitemize
\item
  Backend : Java 7, Spring 4 (Security, Data JPA, MVC), Hibernate,
  JUnit, AssertJ, Mockito, Gradle
\item
  Frontend : JavaScript ES5, AngularJS, Jasmine
\item
  Methodology: Agile Scrum, 4/5 dev
\stopitemize

\startdescription{Feb. 15 - Aug. 16}
  {\bf Golang Development on
  \useURL[url7][https://traefik.io/][][Træfik]\from[url7]};
  \useURL[url8][https://containo.us/][][Containous]\from[url8] - Lyon
  (France)
\stopdescription

6-months end-of-courses internship on
\useURL[url9][https://traefik.io/][][Træfik]\from[url9]. Developing 2
packages which provide configuration interfaces for Golang programs:

\startitemize
\item
  \useURL[url10][https://github.com/containous/flaeg][][Flæg]\from[url10]:
  Dynamic Command Line Interface
\item
  \useURL[url11][https://github.com/containous/staert][][Stært]\from[url11]:
  Reads, Merges and Store configurations
\stopitemize

Tech:

\startitemize
\item
  Backend : Golang 1.7
\item
  Tech devops : Git, Github, Travis CI, Docker, Key/Value Distibuted
  Databases
\item
  Methodology: Open Source Projects, Code Reviews, Pull Requests,
  Startup
\stopitemize

\startdescription{January 2015 - May 2015}
  {\bf Sysadmin development};
  \useURL[url12][http://www.savediffusion.fr/][][SAVE
  Diffusion]\from[url12] - Saint-Etienne (France)
\stopdescription

Development of a network monitoring service (Shinken/Nagios) for a radio
studio network.

\startitemize
\item
  Tech : Linux server, network protocols (SNMP, Ping, \ldots{}), Shell,
  Perl and Python scripts.
\item
  Methodology: Working in 4 students team. AGILE approach.
\stopitemize

\subsection[education]{Education}

\startdescription{2013 - 2016}
  {\bf Engineering degree};
  \useURL[url13][https://www.telecom-st-etienne.fr/][][Télécom
  Saint-Étienne]\from[url13] (FR)

  {\em Specialization in Computer, Network Sciences}
\stopdescription

\startdescription{2015 - 2016}
  {\bf Erasmus student exchange};
  \useURL[url14][https://www.cvut.cz/en][][Czech Technical University in
  Prague]\from[url14] (CZ)

  {\em 1 semester : MSc classes taught in English at the Faculty of
  Information Technologies}
\stopdescription

\startdescription{2011 - 2013}
  {\bf 2-year Initial Engineering Course};
  \useURL[url15][https://www.telecom-st-etienne.fr/][][Télécom
  Saint-Étienne]\from[url15] (FR)

  {\em Double diploma course : Technological Degree in Electronics and
  Computer Engineering, University Diploma in Initial Cycle of
  Information Technologies of St-Etienne}
\stopdescription

\subsection[skills]{Skills}

\startdescription{Programming Languages}
  \startitemize[packed]
  \item
    Java SE/EE 7 & 8, JavaScript ES6, Golang, SQL, HTML5, CSS3
  \stopitemize
\stopdescription

\startdescription{Backend Frameworks}
  \startitemize[packed]
  \item
    Spring(Boot, MVC, Data, Security), JPA, AssertJ, Mockito, ZK, Drools
  \stopitemize
\stopdescription

\startdescription{Frontend Frameworks}
  \startitemize[packed]
  \item
    ReactJS, Redux, Jasmine/Jest, Fetch API, AngularJS, Bootstrap, SASS
  \stopitemize
\stopdescription

\startdescription{DevOps and tools}
  \startitemize[packed]
  \item
    Git, Maven, NPM, Docker, MySql, Apache Kafka, Flume, Tomcat,
    WebLogic
  \item
    Jenkins, Github, Gitlab with CI, Bitbucket, Jira, Intellij,
    Wordpress
  \stopitemize
\stopdescription

\startdescription{Methodologies}
  \startitemize[packed]
  \item
    Agile (Scrum), Code Reviews, Test Driven Development, Pair
    Programming
  \stopitemize
\stopdescription

\subsection[others]{Others}

\startitemize
\item
  Human Languages:

  \startitemize[packed]
  \item
    French (native speaker)
  \item
    English (professional)
  \stopitemize
\item
  Hobbies:
  \startitemize[packed]
  \item
    Handball
  \item
    Mountain(hiking, skiing, biking, climbing)
  \stopitemize
\stopitemize

\thinrule

\startblockquote
\useURL[url16][mailto:martin.piegay@telecom-st-etienne.fr][][martin.piegay@telecom-st-etienne.fr]\from[url16]
• +33 6 25 97 03 83 • 24 years old\crlf
- Lyon, France
\stopblockquote

\stoptext
